Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2015-09-13 documentation/userguide.tex
The code is now configured to run in 2D axisymmetric coordinates. Plus I did a little general cleanup while I was working on that.

@@

  \item \texttt{orbital\_kick}: whether or not to kick the stars with an orbital velocity corresponding to their 

>>>>

Though we are mainly interested in 3D simulations, it is sometimes useful to compare to 2D
simulations which are much cheaper and can be run at higher resolutions. The only physically
meaningful analogue to these mergers in lower dimensions occurs in 2D axisymmetric cylindrical
coordinates. CASTRO represents these as $(r,z,\theta)$. In this coordinate system we enforce
that the stars lie along the $z$ axis and that the center of the stars lies at $r = 0$. The
$\theta$ dimension doesn't get directly evolved hydrodynamically but that is the dimension
along which the rotational motion occurs, so in some circumstances the velocity in that
direction will change with time because we still allow the $\theta$-velocity to participate in
the Coriolis force. When rotation is enabled, the rotation is along the $z = 0$ axis in the $r$
coordinate dimension. To try this out you should use \texttt{DIM = 2} in the makefile and
use \texttt{inputs\_2d} in the \texttt{source/} directory.

@@

  \item \texttt{no\_orbital\_kick}: whether or not to kick the stars with an orbital velocity corresponding to their 
